Diminishing Democratic Ethos in South Korea by Political Dissatisfaction

### 2024-04-19 paper/paper.qmd
Update paper.qmd

---
title: "Perceptions of Democracy in South Korea"
subtitle: "Insights from 2016 Survey Data"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/Democracy_Perception_in_South_Korea.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions. Through the quantitative analysis, the research uncovers a complex relationship between diverse factors and democratic perception, demonstrating how political dissatisfaction can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and political dissatisfaction to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socio-economic and political landscape. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations [@article]. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

This paper delves into the significant question of how economic and political dissatisfaction influence the democratic perceptions of South Korean citizens. To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts. This methodological approach allows for a detailed exploration of political satisfaction influence perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socio-economic dissatisfaction influence democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.

This paper is structured to first provide a detailed literature review that sets the theoretical framework for understanding the impact of globalization on democratic values. Following this, @sec-data and @sec-model describes the survey design and analytical techniques by conducting linear regression model. @sec-result present the analysis results, discuss the findings in the context of existing literature in @sec-discussion with implications for weakness and suggestions for future research.

# Data {#sec-data}
This project used `R` [@citeR] throughout its execution. The `tidyverse` [@tidy] package was utilized for data cleaning and manipulation tasks. The creation of figures and other data visualizations was adeptly handled using `ggplot2` [@ggplot2R], while `knitr` [@knitrR] and `kableExtra` [@kableextra] were used for their excellent data presentation features. File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modeling, along with the `broom` [@robinson] for illustrative purposes.

@@

As show in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1. very satisfied, 2. fairly satisfied, 3. not very satisfied, and 4. not at all satisfied. For the independent variables, key variables on economic satisfaction will include responses to the question, "Would you say that over the past twelve months, the state of the economy in South Korea has gotten much better, gotten somewhat better, stayed about the same, gotten somewhat worse, or gotten much worse?" Answers are coded as 1. Gotten better, 2. stayed the same, 3. gotten worse, 4. don’t know. Additionally, perceptions of corruption will be assessed with the question, "Most politicians are trustworthy." Responses are coded as 1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree. Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government in 2016: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years? Has she done a very good job?" Political satisfaction responses are coded as 1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job.

@@

# Create the data frame with the variable summary
variable_summary <- data.frame(
  Types = c("The dependent variable", "The independent variables", "", ""),
  Variables = c("Dissatisfaction with democracy", "Dissatisfaction with economy", "Distrust level agianst politicians", "Dissatisfaction with politics"),
  Criterion = c(
    "1. Very satisfied, 2. Fairly satisfied, 3. Not very satisfied, 4. Not at all satisfied",
    "1. Gotten better, 2. Stayed the same, 3. Gotten worse, 4. Don’t know",
    "1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree",
    "1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job"
  )
)

@@

In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level agianst Korean politicians, dissatisfaction of economy and politics. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another color representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender group. Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.

@@

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by birth year, which are shown on the x-axis and range from 1931 to 1997. The darkness of the bars corresponds to age, with darker shades representing older age groups.The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians. The younger generations who exhibit higher levels of distrust indicates a growing skepticism about political figures among newer generations compared to their older counterparts. This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.

@@

These figures collectively aim to shed light on the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea. The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance. Next, we will explore how these factors relate to their democratic perception through linear regression model.

@@

In the Bayesian linear rewgression model[@rstanarm], we attempt to predict $Dissatisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Distrust\_level\_against\_politicians$, $Dissatisfaction\_with\_economy$, and $Dissatisfaction\_with\_politics$ as independent variables. The $y_i$ values are assumed to be normally distributed with a mean of $\mu_i$ and a common standard deviation $\sigma$. The mean $\mu_i$ is a linear combination of the independent variables, represented by the equation $\mu_i = \beta_0 + \beta_1 \cdot Dissatisfaction\_with\_economy_i + \beta_2 \cdot Distrust\_level\_against\_politicians_i + \beta_3 \cdot Dissatisfaction\_with\_politics_i$. Here, $\beta_0$ is the intercept, the expected value of $Dissatisfaction\_with\_politics$ when all independent variables are at zero, reflecting a baseline level of satisfaction without the influence of the predictors. The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ are the slopes that measure the expected change in $Dissatisfaction\_with\_politics$ for a one-unit change in their respective independent variables, assuming other variables are held constant. These regression coefficients are assumed to follow normal distributions with means of zero and standard deviations of 2.5, indicating that before observing the data, we believe it is equally likely that the variables could have a positive or negative association with satisfaction, with a moderate level of certainty. The standard deviation $\sigma$ of the dependent variable's distribution captures the variability of $Dissatisfaction\_with\_politics$ around its mean that is not explained by the independent variables. An Exponential prior with a rate of 1 is assigned to $\sigma$, which suggests we expect smaller values of $\sigma$ (indicating less noise) to be more likely than larger ones. This setup of priors and the model framework allow us to incorporate prior beliefs and uncertainties about the parameters, which are then updated with the data to provide a posterior distribution reflecting our updated beliefs.

@@

The @fig-political-perceptions displays a clear positive correlation between dissatisfaction with politics and dissatisfaction with democracy, indicated by the ascending trend line. As political dissatisfaction increases, so does dissatisfaction with democracy, suggesting that negative feelings towards the political system are closely linked with negative perceptions of democratic governance. The gradient color, representing age groups from older (darker) to younger (lighter), reveals a relatively even distribution across the spectrum of political dissatisfaction, signifying that these sentiments are pervasive across different ages without a visible age-related trend in the data. This indicates a general consensus across generations regarding the relationship between political dissatisfaction and democratic discontent.

@@

# Rename the factor levels for better graph labeling
model_coefficients$model <- factor(model_coefficients$model, levels = c("econ", "pol", "trust"),
                                   labels = c("Economic Dissatisfaction", "Political Dissatisfaction", "Distrust Against Politicians"))

>>>>

---
title: "Diminishing Democratic Ethos in South Korea by Political Dissatisfaction"
subtitle: "Insights from 2016 Survey Data"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/Democracy_Perception_in_South_Korea.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions. Through the quantitative analysis, the research uncovers a complex relationship between diverse factors and democratic perception, demonstrating how political dissatisfaction can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and political dissatisfaction to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

In South Korea, a nation where I was born and raised, the rapid and profound impacts of globalization have redefined the socioeconomic and political landscape. As democracy inherently upholds the principle of political equality, ensuring that every citizen has a voice in the political discourse, these global forces present significant challenges. South Korea, characterized by swift economic growth and transformative political shifts, provides a critical context for exploring these challenges. These changes impact more than just the economy; they deeply influence the democratic ethos, raising crucial questions about the sustainability of political equality amidst pervasive transformations [@article]. Thus, the citizens of South Korea find themselves navigating an altered political and economic terrain, necessitating a critical reevaluation of democratic values in response to these global dynamics.

This paper delves into the significant question of how economic and political dissatisfaction influences the democratic perceptions of South Korean citizens. To address our understanding of the contemporary democratic ethos in South Korea, this research utilizes data derived from a comprehensive questionnaire distributed to Korean citizens in 2016, capturing their perceptions of economic and political aspects. Employing linear regression models, the analysis focuses on identifying and interpreting the relationships between citizens' economic conditions and political contexts. This methodological approach allows for a detailed exploration of how political satisfaction influences perceptions and behaviours related to democracy in South Korea.

The findings of this study are vital for understanding the current state and future trajectory of democracy in regions undergoing rapid globalization. By highlighting how socioeconomic dissatisfaction influences democratic engagement, this research offers insights that are crucial for policymakers, scholars, and citizens concerned with fostering a robust democratic society in the face of global changes.

This paper is structured to first provide a detailed literature review that sets the theoretical framework for understanding the impact of globalization on democratic values. Following this, @sec-data and @sec-model describe the survey design and analytical techniques by conducting a linear regression model. @sec-result presents the analysis results, and discusses the findings in the context of existing literature in @sec-discussion with implications for weakness and suggestions for future research.

# Data {#sec-data}
This project used `R` [@citeR] throughout its execution. The `tidyverse` [@tidy] package was utilized for data cleaning and manipulation tasks. The creation of figures and other data visualizations was adeptly handled using `ggplot2` [@ggplot2R], while `knitr` [@knitrR] and `kableExtra` [@kableextra] were used for their excellent data presentation features. File path management was conducted with `readr` [@readrR], and `rstanarm` [@rstanarm] was employed for statistical modelling, along with the `broom` [@robinson] for illustrative purposes.

@@

As shown in @tbl-variables, the dependent variable will be based on the question, "On the whole, are you very satisfied, fairly satisfied, not very satisfied, or not at all satisfied with the way democracy works in South Korea?" The responses are coded on a four-point scale: 1. very satisfied, 2. fairly satisfied, 3. not very satisfied, and 4. not at all satisfied. For the independent variables, key variables on economic satisfaction will include responses to the question, "Would you say that over the past twelve months, the state of the economy in South Korea has gotten much better, gotten somewhat better, stayed about the same, gotten somewhat worse, or gotten much worse?" Answers are coded as 1. Gotten better, 2. stayed the same, 3. gotten worse, 4. don’t know. Additionally, perceptions of corruption will be assessed with the question, "Most politicians are trustworthy." Responses are coded as 1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree. Lastly, data on political changes will be obtained from the question regarding the performance of President Geun-hye Park's government in 2016: "Now thinking about the performance of the government of Geun-hye Park president in general, how good or bad a job do you think the government of Geun-hye Park president did over the past three years? Has she done a very good job?" Political satisfaction responses are coded as 1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job.

@@

# Create the data frame with the variable summary
variable_summary <- data.frame(
  Types = c("The dependent variable", "The independent variables", "", ""),
  Variables = c("Dissatisfaction with democracy", "Dissatisfaction with economy", "Distrust level against politicians", "Dissatisfaction with politics"),
  Criterion = c(
    "1. Very satisfied, 2. Fairly satisfied, 3. Not very satisfied, 4. Not at all satisfied",
    "1. Gotten better, 2. Stayed the same, 3. Gotten worse, 4. Don’t know",
    "1. Strongly agree, 2. Somewhat agree, 3. Neither, 4. Somewhat disagree, 5. Strongly disagree",
    "1. Very good job, 2. Good job, 3. Bad job, 4. Very bad job"
  )
)

@@

In the @fig-gender-perceptions, we have a set of three bar graphs, each representing a different type of distrust level against Korean politicians, and dissatisfaction of economy and politics. The bars are divided by gender, with one colour representing male respondents (labelled as '1') and another colour representing female respondents (labelled as '2'). The y-axis shows the average perception score, which likely corresponds to a survey response scale. Each bar's height indicates the average score for that perception type among the respective gender groups. Both genders have similar average scores for economic dissatisfaction, while there may be slight differences in distrust against politicians and political dissatisfaction.

@@

In the @fig-age-perceptions, the same three types of perceptions are displayed. This time, however, they are categorized by birth year, which is shown on the x-axis and ranges from 1931 to 1997. The darkness of the bars corresponds to age, with darker shades representing older age groups. The @fig-age-perceptions suggest a view of generational sentiments: while economic and political dissatisfaction remain relatively consistent across age groups, there is a notable divergence when it comes to distrust in politicians. The younger generations who exhibit higher levels of distrust indicate a growing skepticism about political figures among newer generations compared to their older counterparts. This shift could reflect the evolving political landscape and the impact of recent events on the trust levels of different age groups.

@@

These figures collectively aim to shed light on the distribution of attitudes towards different aspects of democratic society among different demographic groups in South Korea. The variation in average scores across different genders and age groups may suggest underlying social or cultural factors that influence how different groups perceive economic conditions and political performance. Next, we will explore how these factors relate to their democratic perception through the linear regression model.

@@

In the Bayesian linear regression model[@rstanarm], we attempt to predict $Dissatisfaction\_With\_Democracy$ (the dependent variable, denoted as $y_i$ for each observation $i$) using $Distrust\_level\_against\_politicians$, $Dissatisfaction\_with\_economy$, and $Dissatisfaction\_with\_politics$ as independent variables. The $y_i$ values are assumed to be normally distributed with a mean of $\mu_i$ and a common standard deviation $\sigma$. The mean $\mu_i$ is a linear combination of the independent variables, represented by the equation $\mu_i = \beta_0 + \beta_1 \cdot Dissatisfaction\_with\_economy_i + \beta_2 \cdot Distrust\_level\_against\_politicians_i + \beta_3 \cdot Dissatisfaction\_with\_politics_i$. Here, $\beta_0$ is the intercept, the expected value of $Dissatisfaction\_with\_politics$ when all independent variables are at zero, reflecting a baseline level of satisfaction without the influence of the predictors. The coefficients $\beta_1$, $\beta_2$, and $\beta_3$ are the slopes that measure the expected change in $Dissatisfaction\_with\_politics$ for a one-unit change in their respective independent variables, assuming other variables are held constant. These regression coefficients are assumed to follow normal distributions with means of zero and standard deviations of 2.5, indicating that before observing the data, we believe it is equally likely that the variables could have a positive or negative association with satisfaction, with a moderate level of certainty. The standard deviation $\sigma$ of the dependent variable's distribution captures the variability of $Dissatisfaction\_with\_politics$ around its mean that is not explained by the independent variables. An Exponential prior with a rate of 1 is assigned to $\sigma$, which suggests we expect smaller values of $\sigma$ (indicating less noise) to be more likely than larger ones. This setup of priors and the model framework allow us to incorporate prior beliefs and uncertainties about the parameters, which are then updated with the data to provide a posterior distribution reflecting our updated beliefs.

@@

The @fig-political-perceptions displays a clear positive correlation between dissatisfaction with politics and dissatisfaction with democracy, indicated by the ascending trend line. As political dissatisfaction increases, so does dissatisfaction with democracy, suggesting that negative feelings towards the political system are closely linked with negative perceptions of democratic governance. The gradient colour, representing age groups from older (darker) to younger (lighter), reveals a relatively even distribution across the spectrum of political dissatisfaction, signifying that these sentiments are pervasive across different ages without a visible age-related trend in the data. This indicates a general consensus across generations regarding the relationship between political dissatisfaction and democratic discontent.

@@

# Rename the factor levels for better graph labelling
model_coefficients$model <- factor(model_coefficients$model, levels = c("econ", "pol", "trust"),
                                   labels = c("Economic Dissatisfaction", "Political Dissatisfaction", "Distrust Against Politicians"))
